---
title: "Homework 0"
author: "Richa Jain"
format: html
editor: visual
execute: 
  echo: FALSE
---

```{r}
quadratic_formula <- function(a, b, c){
    discriminant <- (b^2) - (4*a*c)
    
    if(discriminant < 0){
      print("No Real Solution")
    }
    
    else if(discriminant > 0){
      sol1 <- (-b + sqrt(b^2 - 4*a*c))/(2*a)
      sol2 <- (-b - sqrt(b^2 - 4*a*c))/(2*a)
      cat("The two solutions are: (", sol1, ", ", sol2, ")", "\n")
    }
    
    else{
      sol <- -b/(2*a)
      paste0("There is one solution: ", sol)
    }
}
```

# Exercise 1

This provides a solution to the quadratic formula $ax^2 + bx + c = 0$ for various a, b, and c values. The one I calculated is for a=1, b=3, and c=2.

The formula being used is: $x = \frac{{-b \pm \sqrt{{b^2 - 4ac}}}}{{2a}}$

If the determinant ${b^2 - 4ac}$ is \< 0, then there are no real solutions to the quadratic equation. If the determinant is \> 0, there are two real solutions. If the determinant = 0, there is one real solution.

The following solution is for a=1, b=3, and c=2:

```{r}
a <- 1
b <- 3
c <- 2

quadratic_formula(a, b, c)
```

# Exercise 2

This provides a graph of f(x) versus x for $x \epsilon (-5,5)$

The line at y=0 is meant to indicate the solutions to the quadratic equation. The points where the quadratic graph meet the line y=0 are the solutions to the equation. If there are no real solutions, the line and graph will not meet.

```{r}
x <- seq(-5, 5, length=300)
plot(x, a*x^2 + b*x + c, type = "l")
abline(h=0, lty = 2)
```
